\section{Appointment Procedures}

\begin{enumerate}[label*=\thesection.\arabic*.]
    \item Elections for all URN Officers shall be held at the Annual General Meeting (AGM).
          \begin{enumerate}[label*=\arabic*.]
              \item There shall be a single election for the positions of Station Editor and Deputy Station Editor, whereby the winning candidate will be elected as Station Editor, and the runner up will be elected Deputy Station Editor.
          \end{enumerate}
    \item The Returning Officer for all elections shall be the Deputy Station Editor, except where they are a candidate, in which case the Station Executive Committee shall appoint another officer in their place.
    \item Where Officer Positions are unfilled at the AGM, an EGM shall be called within the first four weeks of the Summer Term, where a by-election will be held for those vacant positions.
    \item Unfilled positions can then be filled at the discretion of the incoming Station Management Committee through co-option, with a two-third-majority decision.
    \item If an Officer resigns during the course of their term, nominations should open with seven days to fill the position and a by-election held.
          \begin{enumerate}[label*=\arabic*.]
              \item The Station Management Committee can appoint an Interim Officer whilst this process takes place.
              \item Where an Officer position is unfilled at a by-election, then the Station Management Committee can co-opt members to fill those positions.
          \end{enumerate}
    \item Candidates shall have the opportunity to submit a two hundred word manifesto to the Returning Officer before the close of Nominations, and attend a hustings where candidates will present themselves for one minute, before a question and answer session, which will be at the discretion of the Returning Officer.
    \item Nominations shall close no later than 5:00pm, two Students' Union days before an election.
    \item Only Full Members of URN shall be able to vote within or stand for election.
    \item The voting method for all elections shall be the Single Transferable Vote system.
\end{enumerate}
